Adaptive Solutions (no date) Climate App. Available at: \_\_URL0\_\_ (Accessed: 21 March 2025).

FEMA (2023) Flood Insurance Manual. Federal Emergency Management Agency. Available at: \_\_URL0\_\_ (Accessed: 15 May 2025). Gil, J. and Steinbach, P. (2008) 'From flood risk to indirect flood impact: Evaluation of street network performance for effective management, response and repair', WIT Transactions on Ecology and the Environment, 118, pp. 335--344. doi:10.2495/FRIAR080321. Greater Chennai Corporation (2024) City Disaster Management Perspective Plan 2024. Available at: \_\_URL1\_\_ (Accessed: January 2025). Hillier, B. (2009) 'Spatial sustainability in cities: Organic patterns and sustainable forms', Proceedings of the 7th International Space Syntax Symposium, Stockholm: KTH Royal Institute of Technology. Hillier, B. and Hanson, J. (1987) The Social Logic of Space. Cambridge: Cambridge University Press.



IPCC (2022) Climate Change 2022: Impacts, Adaptation and Vulnerability. Contribution of Working Group II to the Sixth Assessment Report of the Intergovernmental Panel on Climate Change. Cambridge University Press. Available at: \_\_URL0\_\_ (Accessed: 15 May 2025). Lavell, A. (2003) 'La gestión local del riesgo: conceptos y políticas para América Latina', Lima: FLACSO. Maureira, V. and Karimi, K. (2017) 'The everyday and the post-disaster urban systems as one thing: A configurational approach to enhance the recovery and resilience of cities affected by tsunamis', Proceedings of the 11th Space Syntax Symposium, Lisbon: Instituto Superior Técnico, pp. 91.1--91.17. Available at: \_\_URL1\_\_ (Accessed: 21 March 2025). Marsh McLennan (2021) Sunk Cost: The Socioeconomic Impacts of Flooding. Available at: \_\_URL2\_\_ (Accessed: 21 March 2025). Registrar General \& Census Commissioner, India (2011) Census of India 2011. Available at: \_\_URL3\_\_ (Accessed: January 2025). Rentschler, J., Salhab, M. and Jafino, B.A. (2022) 'Flood exposure and poverty in 188 countries', Nature Communications, 13(1), pp. 1--11. doi:10.1038/s41467-022-30727-4. The International Disaster Database (2025) Centre for Research on the Epidemiology of Disasters. Available at: \_\_URL4\_\_ (Accessed: February 2025). Wong, T.H.F. \& Brown, R.R. (2011). Water Sensitive Urban Design. In: Grafton, R.Q. \& Hussey, K. (eds.) Water Resources Planning and Management. Cambridge: Cambridge University Press, pp. 483--504. \_\_URL5\_\_ World Bank (2022) 'Flood risk already affects 1.81 billion people', World Bank Blogs. Available at: \_\_URL6\_\_ (Accessed: 21 March 2025). World Meteorological Organization (2023) Floods: Deadliest Natural Hazards. Available at: \_\_URL7\_\_ (Accessed: 21 March 2025). 

The detailed technical procedures used in the accessibility modelling, including the penalty classification criteria applied to the street network analysis, are provided in Appendix A. Additionally, full-scale maps illustrating the model outputs are presented in Appendix B.
